### 2017-12-11 submission/manuscript.Rmd
add table s4 to results

This Taq dependent difference in the number of OTUs was also observed in the mock community samples with the same Taq polymerases being high (Platinum) and low (Accuprime) respectively [Figure 2 & Table S3]. Conversely, differences between HiFi Taq were observed as early as 20 cycles and a sub-sampling depth of 1000 sequences (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. Across sub-sampling depth and cycle number the lowest number of OTUs identified was generally from Accuprime^TM^ while the highest was from Platinum for both fecal and mock samples [Figure 1 & 2].

***Per Base Error Rate is Dependent on both Taq and Cycle Number Used:***
The median average per base error was highest for the Kappa HiFI Taq [FIgure 3A]. Sub-sampling depth seems to have little effect on this rate with both 5000 and 10000 sub-sampled sequences showing similar results [Figure 3B & C]. Generally, there were small differences between the various HiFi Taq at lower cycle number but larger differences at higher cycle number [Figure 3B & C]. Platinum HiFi Taq consistently had the highes median average per base error rate while Phusion and Accuprime had the lowest [Figure 3B & C]. These differences though were realtively small between the different HiFi Taq [Figure 3]. The total seqeunces with at least one error matched the median average per base error except for the Accuprime HiFi Taq [Figure S1]. Although it had the lowest per base error rate it had either the largest or second largest number of sequences with at least one error regardless of cycle number of sub-sampling depth [Figure S1]. Investigation of whether there were Taq dependent effects on base subsitution found that there was no clear bias and this was indpendent of sub sampling depth [Figure S2-S4]. Further, the variation in subsitution error seems to reduce as the sequencing depth increases [Figure S2-S4].

>>>>

This Taq dependent difference in the number of OTUs was also observed in the mock community samples with the same Taq polymerases being high (Platinum) and low (Accuprime) respectively [Figure 2 & Table S3]. Conversely, differences between HiFi Taq were observed as early as 20 cycles and a sub-sampling depth of 1000 sequences (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. Using a Tukey post-hoc test differences between Platinum and the other HiFi Taqs was the major driver of the differences seen at different cycle numbers and sub-sampling depths [Table S4]. Both fecal and mock samples consistently showed that across sub-sampling depth and cycle number the lowest number of OTUs identified was from Accuprime^TM^ while the highest was from Platinum for both fecal and mock samples [Figure 1 & 2].

***Per Base Error Rate is Dependent on both Taq and Cycle Number Used:***
Differences by HiFi Taq in the median average per base error varied without a clear pattern across sub-sampling depth []. Generally, the highest values were for the Kappa HiFI Taq [Figure 3A]. Sub-sampling depth seems to have little effect on this rate with both 5000 and 10000 sub-sampled sequences showing similar results [Figure 3B & C]. Generally, there were small differences between the various HiFi Taq at lower cycle number but larger differences at higher cycle number [Figure 3B & C]. Platinum HiFi Taq consistently had the highes median average per base error rate while Phusion and Accuprime had the lowest [Figure 3B & C]. These differences though were realtively small between the different HiFi Taq [Figure 3]. The total seqeunces with at least one error matched the median average per base error except for the Accuprime HiFi Taq [Figure S1]. Although it had the lowest per base error rate it had either the largest or second largest number of sequences with at least one error regardless of cycle number of sub-sampling depth [Figure S1]. Investigation of whether there were Taq dependent effects on base subsitution found that there was no clear bias and this was indpendent of sub sampling depth [Figure S2-S4]. Further, the variation in subsitution error seems to reduce as the sequencing depth increases [Figure S2-S4].

### 2017-12-11 submission/manuscript.tex
add table s4 to results

This Taq dependent difference in the number of OTUs was also observed in
the mock community samples with the same Taq polymerases being high
(Platinum) and low (Accuprime) respectively {[}Figure 2 \& Table S3{]}.
Conversely, differences between HiFi Taq were observed as early as 20
cycles and a sub-sampling depth of 1000 sequences (P-value = 0.002)
{[}Table S3{]}. Across sub-sampling depth and cycle number the lowest
number of OTUs identified was generally from
Accuprime\textsuperscript{TM} while the highest was from Platinum for
both fecal and mock samples {[}Figure 1 \& 2{]}.

\textbf{\emph{Per Base Error Rate is Dependent on both Taq and Cycle
Number Used:}} The median average per base error was highest for the
Kappa HiFI Taq {[}FIgure 3A{]}. Sub-sampling depth seems to have little
effect on this rate with both 5000 and 10000 sub-sampled sequences
showing similar results {[}Figure 3B \& C{]}. Generally, there were
small differences between the various HiFi Taq at lower cycle number but
larger differences at higher cycle number {[}Figure 3B \& C{]}. Platinum
HiFi Taq consistently had the highes median average per base error rate
while Phusion and Accuprime had the lowest {[}Figure 3B \& C{]}. These
differences though were realtively small between the different HiFi Taq
{[}Figure 3{]}. The total seqeunces with at least one error matched the
median average per base error except for the Accuprime HiFi Taq
{[}Figure S1{]}. Although it had the lowest per base error rate it had
either the largest or second largest number of sequences with at least
one error regardless of cycle number of sub-sampling depth {[}Figure
S1{]}. Investigation of whether there were Taq dependent effects on base
subsitution found that there was no clear bias and this was indpendent
of sub sampling depth {[}Figure S2-S4{]}. Further, the variation in
subsitution error seems to reduce as the sequencing depth increases
{[}Figure S2-S4{]}.

>>>>

This Taq dependent difference in the number of OTUs was also observed in
the mock community samples with the same Taq polymerases being high
(Platinum) and low (Accuprime) respectively {[}Figure 2 \& Table S3{]}.
Conversely, differences between HiFi Taq were observed as early as 20
cycles and a sub-sampling depth of 1000 sequences (P-value = 0.002)
{[}Table S3{]}. Using a Tukey post-hoc test differences between Platinum
and the other HiFi Taqs was the major driver of the differences seen at
different cycle numbers and sub-sampling depths {[}Table S4{]}. Both
fecal and mock samples consistently showed that across sub-sampling
depth and cycle number the lowest number of OTUs identified was from
Accuprime\textsuperscript{TM} while the highest was from Platinum for
both fecal and mock samples {[}Figure 1 \& 2{]}.

\textbf{\emph{Per Base Error Rate is Dependent on both Taq and Cycle
Number Used:}} Differences by HiFi Taq in the median average per base
error varied without a clear pattern across sub-sampling depth {[}{]}.
Generally, the highest values were for the Kappa HiFI Taq {[}Figure
3A{]}. Sub-sampling depth seems to have little effect on this rate with
both 5000 and 10000 sub-sampled sequences showing similar results
{[}Figure 3B \& C{]}. Generally, there were small differences between
the various HiFi Taq at lower cycle number but larger differences at
higher cycle number {[}Figure 3B \& C{]}. Platinum HiFi Taq consistently
had the highes median average per base error rate while Phusion and
Accuprime had the lowest {[}Figure 3B \& C{]}. These differences though
were realtively small between the different HiFi Taq {[}Figure 3{]}. The
total seqeunces with at least one error matched the median average per
base error except for the Accuprime HiFi Taq {[}Figure S1{]}. Although
it had the lowest per base error rate it had either the largest or
second largest number of sequences with at least one error regardless of
cycle number of sub-sampling depth {[}Figure S1{]}. Investigation of
whether there were Taq dependent effects on base subsitution found that
there was no clear bias and this was indpendent of sub sampling depth
{[}Figure S2-S4{]}. Further, the variation in subsitution error seems to
reduce as the sequencing depth increases {[}Figure S2-S4{]}.
